Many Analystis Project

### 2022-02-02 analysis.Rmd
updated

---
title: "Many Analystis Project"
description: 
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-APRIL-29 
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
    highlight: kate
---

@@

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())]
```

@@

First, we import the data (see functions).

@@

### IPW Anxiety ~ Belief

@@

### IPW Anxiety ~ Church

@@

## Results summary Anxiety ~ Belief

@@

## Results summary: Anxiety ~ church

@@

## Results summary Belief ~ Anxiety

@@

<!-- ```{r} -->
<!-- this is no better -->
<!-- m3a<- brm( -->
<!--   bg_s ~ -->
<!--     anx_s+ -->
<!--     ch_s + -->
<!--     age_s  + -->
<!--     male + -->
<!--     (1 + anx_s | country), -->
<!--   data = d1, -->
<!--   seed = 1234, -->
<!--   warmup = 1000, -->
<!--   iter = 3000, -->
<!--   chains = 4, -->
<!--   file = here::here("models", "m3a") -->
<!-- ) -->

<!-- parameters::model_parameters(m3a, test = "p_direction") -->
<!-- brms::ranef(m3a) -->
<!-- summary(m3a) -->
<!-- hist(d1$bg_s) -->
<!-- # YES -->
<!-- pp_check(m3a) -->
<!-- ``` -->

@@

## Results summary Church ~ Anxiety

@@

˝## Simulation tables

@@

<!-- ```{r, cache = TRUE} -->
<!-- rel %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot() + theme_blackboard() -->
<!-- ``` -->

@@

<!-- ```{r cache = TRUE} -->
<!-- wbgen %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot() + theme_blackboard() -->
<!-- ``` -->

@@

<!-- ```{r} -->
<!-- wbphys %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   summary() -->

<!-- wbphys %>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot() + theme_blackboard() -->
<!-- ``` -->

@@

<!-- ```{r} -->
<!-- wbpsych %>% -->
<!--   select(-wb_psychMEANING)%>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   summary() -->

<!-- wbpsych %>% -->
<!--   select(-wb_psychMEANING)%>% -->
<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->
<!--   plot()  + theme_abyss() -->
<!-- ``` -->

>>>>

---
title: "Many Analystis Project"
description: 
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-APRIL-29 
bibliography: references.bib
link-citations: true
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
    highlight: kate
---

@@

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

First, we import the data (see functions). [@tchetgen2012]

@@

### IPW Anxiety \~ Belief

@@

### IPW Anxiety \~ Church

@@

## Results summary Anxiety \~ Belief

@@

## Results summary: Anxiety \~ church

@@

## Results summary Belief \~ Anxiety

@@

<!-- this is no better -->

<!-- m3a<- brm( -->

<!--   bg_s ~ -->

<!--     anx_s+ -->

<!--     ch_s + -->

<!--     (1 + anx_s | country), -->

<!--   file = here::here("models", "m3a") -->

<!-- parameters::model_parameters(m3a, test = "p_direction") -->

<!-- brms::ranef(m3a) -->

<!-- summary(m3a) -->

<!-- hist(d1$bg_s) -->

<!-- pp_check(m3a) -->

@@

## Results summary Church \~ Anxiety

@@

˝#\# Simulation tables

@@

<!-- rel %>% -->

<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->

<!--   plot() + theme_blackboard() -->

@@

<!-- wbgen %>% -->

<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->

<!--   plot() + theme_blackboard() -->

@@

<!-- wbphys %>% -->

<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->

<!--   summary() -->

<!-- wbphys %>% -->

<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->

<!--   plot() + theme_blackboard() -->

@@

<!-- wbpsych %>% -->

<!--   select(-wb_psychMEANING)%>% -->

<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->

<!--   summary() -->

<!-- wbpsych %>% -->

<!--   select(-wb_psychMEANING)%>% -->

<!--   correlation( partial = FALSE, multilevel = TRUE ) %>% -->

<!--   plot()  + theme_abyss() -->
